Report and Figures

### 2016-11-11 figs.Rmd
updates to loss curve illustrations

cities <- c('Atlanta','Philadelphia', 'Detroit')

@@

sub_curves %>% 
	ggplot() +
	geom_path(aes(x = nclust, y = I_XY, group = city, color = city)) +
	scale_x_continuous(trans = 'log10', limit = c(1, NA), expand = c(0, 0)) +
	scale_y_continuous(limit = c(0,max(sub_curves$I_XY + 0.02)), expand = c(0, 0)) +
	theme_light() +
  theme(text=element_text(size=16),
        panel.margin = unit(2, "lines"),
        panel.border = element_blank(),
        strip.background = element_rect(fill = "white", color = "white", size = 2),
        strip.text.x = element_text(size = 16, color = 'black')) + 
	annotation_logticks(size = .1, sides = 'b', scaled = T) + 
	geom_rect(data = rects, aes(xmin = xmin,
								ymin = ymin,
								xmax = xmax,
								ymax = ymax,
								group = city,
								color = city),
			  # color = 'grey',
			  alpha = 0,
			  size = 0.25) +
	# geom_text(aes(x = nclust, y = I_XY, label = city, hjust = -.2), data = end_points) + 
	geom_polygon(aes(nclust, I_XY, fill = city), data = filled, alpha = .2) + 
	geom_text(aes(x = 50, y = .15, label = paste('AUC = ', round(AUC,2))), data = sub_summary, size = 6) + 
	# geom_text(aes(x = 50, y = .1, label = paste('J(X,Y) = ', round(J_XY,2))), data = sub_summary) +
	facet_wrap(~city) + 
  scale_fill_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  scale_color_brewer(palette = 'Set1', name = NULL, guide = 'none') + 
	# scale_color_discrete(guide = F) + 
	xlab('Number of clusters (n)') + 
	ylab(expression(I(C[n],Y)))

ggsave('figs/AUC_illustration.pdf', width = 10, height = 4)
embed_fonts('figs/AUC_illustration.pdf', outfile = 'figs/AUC_illustration.pdf')
```

@@

adjust_thresh = 0.01
highlights  <- c('Philadelphia', 'Atlanta', 'Detroit')
curves <- binary_loss_curves %>% 
  mutate(exclude = (nclust != 1) & (cummax(I_XY - lag(I_XY,default = 0)) < adjust_thresh) & (nclust < 10)) %>% 
	filter(!exclude,
	       max(I_XY > 0.0)) %>%
	mutate(nclust = row_number())

@@

end_points <- data.frame(city = c('Atlanta', 'Philadelphia', 'Detroit'),
                         nclust = c(50, 7, 8),
                         I_XY = c(.34, .18, .37))

@@

background %>% 
  ggplot(aes(x = nclust, y = I_XY)) +
  geom_path(aes(group = city), color = 'grey', alpha = 0.6) + 
  geom_path(aes(group = city, color = city), data = highlighted) +
  geom_text(aes(label = city), data = end_points) +
  theme_light() +
  scale_x_continuous(trans = 'log10', limits = c(1,NA), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,.5), expand = c(0, 0)) + 
  scale_color_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  xlab('Number of clusters (n)') + 
	ylab(expression(I(C[n],Y))) +
  # geom_vline(xintercept=2, alpha = .2) + 
  annotation_logticks(sides = 'b', size = .2)

@@

adjust_thresh = 0.01
highlights  <- c('Philadelphia', 'Atlanta', 'Detroit')
curves <- loss_curves %>% 
  mutate(exclude = (nclust != 1) & (cummax(I_XY - lag(I_XY,default = 0)) < adjust_thresh) & (nclust < 10)) %>% 
	filter(!exclude,
	       max(I_XY > 0.0)) %>%
	mutate(nclust = row_number())

@@

end_points <- data.frame(city = c('Atlanta', 'Philadelphia', 'Detroit'),
                         nclust = c(50, 7, 8),
                         I_XY = c(.36, .19, .44))

@@

background %>% 
  ggplot(aes(x = nclust, y = I_XY)) +
  geom_path(aes(group = city), color = 'grey', alpha = 0.6) + 
  geom_path(aes(group = city, color = city), data = highlighted) +
  geom_text(aes(label = city), data = end_points) +
  theme_light() +
  scale_x_continuous(trans = 'log10', limits = c(1,NA), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,.7), expand = c(0, 0)) + 
  scale_color_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  xlab('Number of clusters (n)') + 
	ylab(expression(I(C[n],Y))) +
  # geom_vline(xintercept=2, alpha = .2) + 
  annotation_logticks(sides = 'b', size = .2)

@@

city <- 'Detroit'
print(city)
nclusters <- 1:6
g <- prominence_map(city, races)
g <- g %>% cluster_map(city, races, nclusters)

@@

>>>>

cities <- c('Atlanta','Philadelphia', 'Detroit', 'Chicago')

@@

sub_curves %>% 
	ggplot() +
	geom_path(aes(x = nclust, y = I_XY, group = city, color = city)) +
	scale_x_continuous(trans = 'log10', limit = c(1, NA), expand = c(0, 0)) +
	scale_y_continuous(limit = c(0,max(sub_curves$I_XY + 0.02)), expand = c(0, 0)) +
	theme_light() +
  theme(text=element_text(size=16),
        panel.margin = unit(2, "lines"),
        panel.border = element_blank(),
        strip.background = element_rect(fill = "white", color = "white", size = 2),
        strip.text.x = element_text(size = 16, color = 'black')) + 
	annotation_logticks(size = .1, sides = 'b', scaled = T) + 
	geom_rect(data = rects, aes(xmin = xmin,
								ymin = ymin,
								xmax = xmax,
								ymax = ymax,
								group = city,
								color = city),
			  # color = 'grey',
			  alpha = 0,
			  size = 0.25) +
	# geom_text(aes(x = nclust, y = I_XY, label = city, hjust = -.2), data = end_points) + 
	geom_polygon(aes(nclust, I_XY, fill = city), data = filled, alpha = .2) + 
	geom_text(aes(x = 50, y = .15, label = paste('AUC = ', round(AUC,2))), data = sub_summary, size = 6) + 
	# geom_text(aes(x = 50, y = .1, label = paste('J(X,Y) = ', round(J_XY,2))), data = sub_summary) +
	facet_wrap(~city, ncol = 2) + 
  scale_fill_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  scale_color_brewer(palette = 'Set1', name = NULL, guide = 'none') + 
	# scale_color_discrete(guide = F) + 
	xlab('Number of clusters (n)') + 
	ylab(expression(I(C[n],Y)))

ggsave('figs/AUC_illustration.pdf', width = 7, height = 5.5)
embed_fonts('figs/AUC_illustration.pdf', outfile = 'figs/AUC_illustration.pdf')
```

@@

adjust_thresh = 0.01
highlights  <- c('Philadelphia', 'Atlanta', 'Detroit', 'Chicago')
curves <- binary_loss_curves %>% 
  mutate(exclude = (nclust != 1) & (cummax(I_XY - lag(I_XY,default = 0)) < adjust_thresh) & (nclust < 10)) %>% 
	filter(!exclude,
	       max(I_XY > 0.0)) %>%
	mutate(nclust = row_number())

@@

end_points <- data.frame(city = c('Atlanta', 'Philadelphia', 'Detroit', 'Chicago'),
                         nclust = c(50, 7, 8, 1000),
                         I_XY = c(.35, .175, .38, .42))

@@

background %>% 
  ggplot(aes(x = nclust, y = I_XY)) +
  geom_path(aes(group = city), color = 'grey', alpha = 0.6) + 
  geom_path(aes(group = city, color = city), data = highlighted) +
  geom_label(aes(label = city, fill = city), data = end_points) +
  theme_light() +
  scale_x_continuous(trans = 'log10', limits = c(1,NA), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,.5), expand = c(0, 0)) + 
  scale_color_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  scale_fill_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  xlab('Number of clusters (n)') + 
	ylab(expression(I(C[n],Y))) +
  # geom_vline(xintercept=2, alpha = .2) + 
  annotation_logticks(sides = 'b', size = .2)

@@

adjust_thresh = 0.01
highlights  <- c('Philadelphia', 'Atlanta', 'Detroit', 'Chicago')
curves <- loss_curves %>% 
  mutate(exclude = (nclust != 1) & (cummax(I_XY - lag(I_XY,default = 0)) < adjust_thresh) & (nclust < 10)) %>% 
	filter(!exclude,
	       max(I_XY > 0.0)) %>%
	mutate(nclust = row_number())

@@

end_points <- data.frame(city = c('Atlanta', 'Philadelphia', 'Detroit', 'Chicago'),
                         nclust = c(50, 7, 8, 1000),
                         I_XY = c(.36, .19, .46, 0.66))

@@

background %>% 
  ggplot(aes(x = nclust, y = I_XY)) +
  geom_path(aes(group = city), color = 'grey', alpha = 0.6) + 
  geom_path(aes(group = city, color = city), data = highlighted) +
  geom_label(aes(label = city, fill = city), data = end_points) +
  theme_light() +
  scale_x_continuous(trans = 'log10', limits = c(1,NA), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,.7), expand = c(0, 0)) + 
  scale_color_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  scale_fill_brewer(palette = 'Set1', name = NULL, guide = 'none') +
  xlab('Number of clusters (n)') + 
	ylab(expression(I(C[n],Y))) +
  # geom_vline(xintercept=2, alpha = .2) + 
  annotation_logticks(sides = 'b', size = .2)

@@

```{r}
city <- 'Detroit'
print(city)
nclusters <- 1:6
g <- prominence_map(city, races)
g <- g %>% cluster_map(city, races, nclusters)

@@

```{r}
for(city in c('Chicago', 'Atlanta', 'Detroit', 'Philadelphia')){
  print(city)

  out_dir <- paste0('figs/prominence_map_', city, '.pdf')

  out_dir <- paste0('figs/cluster_map_', city, '.pdf')
  ggsave(out_dir, width = 14, height = 14, units = 'cm')
  embed_fonts(out_dir, outfile=out_dir)
}
```
